# Descriptive Statistics for Investment Events

How and when do users invest in trade leaders (TL)?

```{r, echo=FALSE}
require(knitr)
opts_knit$set(root.dir='~/Data/Currensee/')
opts_chunk$set(fig.width=8, fig.height=5)
setwd('~/Data/Currensee')
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(data.table)
library(ggplot2)
library(txtplot)
library(reshape2)
library(igraph)

rm(list=ls())
options(max.print=5000)

investment.events <- readRDS('Rds/investment-events.Rds')
ld <- readRDS('Rds/linkdata.Rds')

```

The trade leader data contains `r investment.events[, length(unique(user_id))]` users
over `r investment.events[, length(unique(brokerAccount_id))]` broker accounts,
of a total 10289 users and 15113 broker accounts on the site.
Investors operated 3955 total broker accounts, including some not used for TL investment.
They invest in `r investment.events[, length(unique(tl_baid))]` trade leader accounts,
owned by `r investment.events[, length(unique(tl_user_id))]` TLs.
About 10% of trades made by investing accounts appear to have been made
independently of a TL. The remainder tracked a broker position.


### What fraction of users reinvest in a TL after uninvesting in them?

```{r}
# reinvestment
setkey(investment.events, brokerAccount_id, tl_baid, etime)
invisible(investment.events[, reinvest := cumsum(isinvest) > 1,
                            by=list(brokerAccount_id, tl_baid)])

# how many users have reinvestment events?
summary(investment.events[, list(any.reinvest=any(reinvest)), by=brokerAccount_id])

```

Most users have only a single investment spell in any trade leader. One quarter, though,
do appear to have multiple investment spells.

### How many contemporaneous investments do users have?

```{r}
# contemporaneous investments
setkey(investment.events, brokerAccount_id, etime)
invisible(investment.events[, cum.investments := cumsum(2 * isinvest - 1),
                            by=brokerAccount_id])

# statistics are 'per user'
summary(investment.events[, list(min.contemp=min(cum.investments),
                                 max.contemp=max(cum.investments),
                                 p25.contemp=quantile(cum.investments,0.25),
                                 p75.contemp=quantile(cum.investments,0.75)
                                 ), by=brokerAccount_id])

```

Users appear to have relatively few contemporaneous investments:
the median user has at most 3 investments, and the 75%-ile user has at most 4
open at any one time.

### How many trade leaders does the average user broker account invest in?

```{r}
accts.invested.by.ba <- investment.events[, list(n_tl_baid=length(unique(tl_baid)),
                                                 n_tl_user_id=length(unique(tl_user_id))),
                                          by=brokerAccount_id]

summary(accts.invested.by.ba)
ggplot(accts.invested.by.ba, aes(n_tl_baid)) + 
    labs(title='# of TLs (broker accounts) users invest in') + 
    xlab('# broker accounts user invests in') +
    geom_density()

ggplot(accts.invested.by.ba, aes(n_tl_user_id)) + 
    labs(title='# of TLs (user ids) users invest in') + 
    xlab('# user accounts user invests in') +
    geom_density()

```

Most users appear to invest in a relatively small number of TLs:
the median user invests in 4, and the distribution is skewed towards zero.
Still, the distribution suggests that most users do some shopping around,
or at least have points of comparison.

Note that the upper tail is dominated by Company staff --
e.g. the top 5 users who invest in the most TL's are a Company dummy account,
the VP of TL management, and the CEO of the company.


### How long are investment spells?

```{r}
max.eday <- as.numeric(as.POSIXct('2014-01-01 24:00:00')) / 86400

setkey(investment.events, brokerAccount_id, tl_baid, etime)
invisible(investment.events[, spellid := cumsum(isinvest),
                            by=list(brokerAccount_id, tl_baid)])
spell.lengths <- investment.events[, list(completed.spell=.N==2,
                                          spell.time=eday[.N] - eday[1],
                                          spell.toend=max.eday - eday[1]),
                                   by=list(brokerAccount_id, tl_baid, spellid)]
invisible(spell.lengths[(!completed.spell), spell.time := spell.toend])

# there appears to be one broken spell, reported as starting in january 1970
# might be an off by factor of 1000 error by company
invisible(spell.lengths[spell.time > 365 * 5, spell.time := NA])

ggplot(spell.lengths, aes(x=spell.time, y=..scaled.., fill=completed.spell)) +
    scale_fill_brewer(type='qual', name='Spell Ended?') + 
    labs(title='Distribution of Investment Spell Length by Continuing Status') + 
    xlab('Spell length (days)') +
    geom_density()

```

Most completed spells appear to be short, as though people are trying out TLs 
for a brief period of time. On the other hand, the data here may be falsely 
including TL accounts that closed -- these won't register an investment closure
event for a user, so I may need an alternative way to detect them.


### Do any TLs invest in other TLs?

```{r}
tl.user_ids <- investment.events[, unique(tl_user_id)]
invests.by.tl <- investment.events[user_id %in% tl.user_ids]

invests.by.tl[, unique(user_id)]

```

Three investors were at one point trade leaders themselves:
user 1 is a co-founder of the company, while users 11179 and 296 appear to be
genuine members of the community.

### Are any TLs friends?

```{r}
tl.friendships <- ld[user_id %in% tl.user_ids & alter_id %in% tl.user_ids]

g <- graph.data.frame(tl.friendships)

plot(g, vertex.size=4, vertex.label=NA,
     edge.arrow.mode='-')

```

There are `r nrow(tl.friendships)/2` friendship ties among 
`r tl.friendships[, length(unique(user_id))]` TLs.

