# Clean and check raw tables, then build out tables for subsequent analysis

Set knitr options:

```{r}
require(knitr)
opts_knit$set(root.dir='~/Data/Currensee/tables-2014/Rds')
```

Load data:

```{r}
library(data.table)

setwd('~/Data/Currensee/tables-2014/Rds')

rm(list=ls())
options(max.print=2000)
```

Load broker accounts table, to get broker account/user mapping

```{r}
ba <- readRDS('BrokerAccount.Rds')
ba <- ba[,list(brokerAccount_id=id, user_id, baseCurrency)]
setkey(ba,brokerAccount_id)
```

Load forex position tracker table, for the meat of the problem.
Drop a bunch of (apparently) useless columns.

```{r}
# make fpt
fpt <- readRDS('ForexPositionTracker.Rds')
# fpt[,c('version','correlationId','position_id','original_id','residual_id',
#        'followedClose','brokerOrderId','stopEnterPrice','rollovers',
#        'dollarPnlExclusions','pipsPnl','closeExecutionCount',
#        'followedTrade_id','openBrokerTradePositionId','closeBrokerTradePositionId',
#        'openPersistTime','closePersistTime') := NULL]
fpt[,c('version','correlationId','position_id','original_id','residual_id',
       'followedClose','brokerOrderId','stopEnterPrice','rollovers',
       'dollarPnlExclusions','pipsPnl','closeExecutionCount',
       'followedTrade_id','openBrokerTradePositionId','closeBrokerTradePositionId',
       'openPersistTime','closePersistTime') := NULL]
# fpt <- fpt[status=='CLOSED', !"status", with=FALSE]
gc()
```

Merge in user ids

```{r}
# add in user ids everywhere...
setkey(fpt, brokerAccount_id)
fpt <- merge(fpt, ba, all.x=TRUE)
stopifnot(all(fpt[,!is.na(user_id)]))
```

Find out how we can track followed trades

```{r}
# inspect close/open Cause_ids
# 3306275 total: 2.87 mil std follow, 432k nothing, 391 ended relationship, 134 ext close, 800 drawdown
summary(fpt[openCause_id == closeCause_id])
# 1218 total: 1067 std follow, 151 nothing
summary(fpt[openCause_id != closeCause_id])
# 4709250 total: 4.708 mil nothing, 473 ext close, 330 user init
summary(fpt[is.na(openCause_id) & is.na(closeCause_id)])
# 425 total: 425 std follow
summary(fpt[is.na(openCause_id) & !is.na(closeCause_id)])
# 103497 total: 50k nothing, 13k ended relationship, 17k drawdown, 20k ext close
summary(fpt[!is.na(openCause_id) & is.na(closeCause_id)])

# check that openCause_ids map into fpt ids
setkey(fpt,id)
fpt.follower <- fpt[!is.na(openCause_id)]
oc.ids <- fpt.follower[, openCause_id]
fpt.followed <- fpt[J(oc.ids)]
stopifnot(length(oc.ids) == nrow(fpt.followed))
# this includes ~ 7218 open originating trades

# some summary stats
# 127 unique trade leaders, 3308 followers, 10289 total users
length(fpt.followed[, unique(user_id)])
length(fpt.follower[, unique(user_id)])
length(fpt[, unique(user_id)])
```

## Make trade leader event series
----------

Get list of all follower trades along with info about who was followed.

```{r}
followed.info <- fpt.followed[, list(openCause_id=id, tl_user_id=user_id, tl_baid=brokerAccount_id,
                                     tl_commission=commission)]
setkey(followed.info, openCause_id)
followed.info <- unique(followed.info)
setkey(fpt.follower, openCause_id)
fpt.follower <- merge(fpt.follower, followed.info, all.x=TRUE)
```

How many broker account - broker account dyads are there? How many user-user?

```{r}
ba.dyads <- fpt.follower[, list(N=.N), by=list(brokerAccount_id, tl_baid)]
user.dyads <- fpt.follower[, list(N=.N), by=list(user_id, tl_user_id)]

ba.reasons <- fpt.follower[, list(N=.N,
                                  minotime=min(openTime, na.rm=TRUE),
                                  minctime=min(closeTime, na.rm=TRUE),
                                  maxotime=max(openTime, na.rm=TRUE),
                                  maxctime=max(closeTime, na.rm=TRUE)
                                  ), by=list(brokerAccount_id, tl_baid, closureReason)]
user.reasons <- fpt.follower[, list(N=.N,
                                    minotime=min(openTime, na.rm=TRUE),
                                    minctime=min(closeTime, na.rm=TRUE),
                                    maxotime=max(openTime, na.rm=TRUE),
                                    maxctime=max(closeTime, na.rm=TRUE)
                                    ), by=list(user_id, tl_user_id, closureReason)]

summary(ba.reasons)
summary(user.reasons)

setkey(ba.reasons, brokerAccount_id, tl_baid)
setkey(user.reasons, user_id, tl_user_id)

summary(fpt.follower[closureReason=='', openTime])
summary(fpt.follower[closureReason!='', openTime])

```



```{r, eval=FALSE}
# setnames(fpt, c('openPrice','openTime','closePrice','closeTime',
#            'dollarPnl','tradePnl','openBalance'),
#          c('openprice','opendate','closeprice','closedate',
#            'dollarpnl','tradepnl','openbalance'))
# fpt[,longtr := 2 * as.numeric(direction=='LONG') - 1]
# fpt[,clopdiff := closeprice - openprice]
# fpt[,pctreturn := (clopdiff / openprice) * longtr]
# fpt <- fpt[!is.na(pctreturn)]

# split out follower trades
fpt.f <- fpt[!is.na(openCause_id) | !is.na(closeCause_id)]
fpt <- fpt[is.na(openCause_id) & is.na(closeCause_id)]
fpt <- fpt[closureReason == '']
fpt.f[is.na(openCause_id), openCause_id := closeCause_id]
setkey(fpt,id)

fpt.f2 <- fpt.f[,list(followers = .N), by=list(id=openCause_id)]
setkey(fpt.f2,id)

fpt <- merge(fpt,fpt.f2,all.x=TRUE)
fpt[,indeptrade := as.numeric(is.na(followers))]

# merge in user ids
setkey(fpt,brokerAccount_id)
fpt <- merge(fpt,ba,all.x=TRUE)

# save and clean
saveRDS(fpt,'../../forexposition.Rds')
rm(fpt, fpt.f, fpt.f2); gc()



# make dbap
dbap <- readRDS('DailyBrokerAccountPerformance.Rds')
dbap[,c('version','intraDayHigh','intraDayLow','maxDD','peakHigh','peakLow',
        'todateClosedRoi','todateNetRoi') := NULL]

# merge in user ids
setkey(dbap,brokerAccount_id)
dbap <- merge(dbap,ba,all.x=TRUE)

# save and clean
saveRDS(dbap,'../../dailybrokeraccount.Rds')
rm(dbap); gc()





# make ld
fl <- readRDS('FriendLink.Rds')
um <- readRDS('UserMessage.Rds')

fl[,c('id','version') := NULL]
um <- um[type=='FRIEND_LINK_REQUEST',list(sender_id, recipient_id, senddate=sendDate)]
setnames(fl,c('friend1_id','friend2_id'),
         c('user_id','alter_id'))
setnames(um,c('sender_id','recipient_id'),
         c('user_id','alter_id'))

# symmetrize
fl <- rbind(fl,fl[,list(user_id=alter_id, alter_id=user_id)], use.names=TRUE)
um <- rbind(um,um[,list(user_id=alter_id, alter_id=user_id, senddate)], use.names=TRUE)

# take last date by friendship
um <- um[,list(senddate=max(senddate)), by=list(user_id,alter_id)]

# merge in dates...
setkey(fl,user_id,alter_id)
setkey(um,user_id,alter_id)
ld <- merge(fl,um,all.x=TRUE)

ld <- ld[!is.na(senddate)]

# save and clean
saveRDS(ld,'../../linkdata.Rds')
rm(fl, um, ld); gc()
```
